Despite my efforts, the success of this project depends largely on the encouragement and guidance of my mentors. I would like to take this opportunity to express my gratitude to the people who are playing a vital role in the successful completion of this project.

\vspace{1em}

My sincere thanks to \textbf{Prof. Dr. Mohammed Shakhawat Hossain}, Principal of DIIT for giving me an opportunity to undertake this project.

\vspace{1em}

My cordial thanks to my Project Supervisor \textbf{Md. Mushfiqur Rahaman}, Lecturer, Department of Computer Science \& Engineering, DIIT for his valuable guidance and support to meet the successful completion of my project.

\vspace{1em}

My sincere thanks to \textbf{Md. Imran Hossain}, Department Head of the Computer Science \& Engineering Department, DIIT for giving me an opportunity to undertake this project. 

\vspace{1em}

My sincere thanks to \textbf{Poly Bhoumik}, Senior Lecturer, Department of Computer Science \& Engineering, DIIT for appreciating my goal. I also express my gratitude to \textbf{Saidur Rahman}, Senior Lecturer and Coordinator, Department of Computer Science \& Engineering, DIIT for appreciating my goal. I also express my gratitude to \textbf{Nusrhat Jahan Sarker}, \textbf{Mizanur Rahman}, \textbf{Moumita Akter}, and \textbf{Ramen Kumar Das}, Lecturer, Department of Computer Science \& Engineering, DIIT for appreciating my goal.

\vspace{1em}

I extend my sincere thanks to my family and friends for their constant support throughout this project. 

\vspace{1em}

Finally, I would be grateful to the \textbf{National University, Bangladesh}, and the coordinator of the \textbf{Bachelor of Science in Computer Science and Engineering} degree program for giving me this opportunity to apply the knowledge that I have gained through the study.
